Supporting Information:\\ NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2019-02-18 Manuscript/manuscriptPSsuppl.tex
Update pdf

\subsection{MacRog}
\noindent
{\it POPC bilayers.} 
% \todo{For example this data set has pretty good description of simulation details in the
% reference. I am not sure how much we should repeat these in here.}
The POPC bilayer consisting of a total of 128 lipids was constructed from single lipid structure taken 
from Ref.~\citenum{kulig15c}. The bilayer was hydrated by a total of 5120 water 
molecules, corresponding to 40 water molecules per lipid.
The MacRog lipid parameters \cite{kulig15b}, obtained from Ref.~\citenum{kulig15c}, were used,
along with the TIP3P water model~\cite{jorgensen83}. The simulation parameters were identical to those used for 
POPC/POPC mixtures with the MacRog force field, see below. The simulation was run for 200~ns using Gromacs 2016.3~\cite{abraham15}, 
out of which 150~ns were used for analyses. The simulation data and related files are available from Ref. \citenum{macrogPOPC298K}.

@@

\subsection{Slipids}
\todo{To be written by Piggot and Favela}
{\it DOPC with 288 lipids.}
The starting structure for simulation was contructed with the MEMBRANE BUILDER website~\cite{ghahremanpour13}: 288 DOPS lipids, 11232 water molecules and 288 Na ions. The Slipids~\cite{jambeck12,jambeck2012another} forcefield was used for DOPS, the TIP3P~\cite{jorgensen83} water model was used to solvate the system and Ions are described by the parameters derived by Aqvist~\cite{aqvist90}.
Simulation was performed for 200~ns, and the last 100~ns were used for the analysis. Simulation was carried out within the NPT ensemble using the GROMACS 5.0.4 package~\cite{abraham2015gromacs}. Timestep of 2~fs was used with the leapfrog integrator. The Nos\'{e}--Hoover thermostat~\cite{nose84,hoover85} was used with reference temperature of 303~K and a relaxation time constant of 0.5~ps; lipids and water plus ions were coupled separately to the heat bath. Pressure was kept constant at 1.013~bar using a semi--isotropic Parrinello--Rahman
barostat~\cite{parrinello81} with a time constant of 10.0~ps. Long-range electrostatic interactions were calculated using the PME method~\cite{darden93,essman95}. A real space cut-off of 1.0~nm was employed with grid spacing of 0.12~nm in the reciprocal space. Lennard-Jones potentials were cut off at 1.4~nm, with a dispersion correction applied to both energy and pressure. All covalent bonds in lipids were constrained using the LINCS algorithm~\cite{hess97}, whereas water molecules were constrained using SETTLE~\cite{miyamoto92}. Twin-range cutoffs, 1.0~nm and 1.6~nm, were used for the neighbor lists with the long-range neighbor list updated every 10 steps.

>>>>

\subsection{MacRog}
\noindent
{\it POPC bilayers.} 
% \todo{For example this data set has pretty good description of simulation details in the
% reference. I am not sure how much we should repeat these in here.}
The POPC bilayer consisting of a total of 128 lipids was constructed from single lipid structure taken 
from Ref.~\citenum{kulig15c}. The bilayer was hydrated by a total of 5120 water 
molecules, corresponding to 40 water molecules per lipid.
The MacRog lipid parameters \cite{kulig15b}, obtained from Ref.~\citenum{kulig15c}, were used,
along with the TIP3P water model~\cite{jorgensen83}. The simulation parameters were identical to those used for 
POPC/POPC mixtures with the MacRog force field, see below. The simulation was run for 200~ns using Gromacs 2016.3~\cite{abraham2015gromacs}, 
out of which 150~ns were used for analyses. The simulation data and related files are available from Ref. \citenum{macrogPOPC298K}.

@@

\subsection{Slipids}
{\it DOPC with 288 lipids.}
The starting structure for simulation was contructed with the MEMBRANE BUILDER website~\cite{ghahremanpour13}: 288 DOPS lipids, 11232 water molecules and 288 Na ions. The Slipids~\cite{jambeck12,jambeck2012another} forcefield was used for DOPS, the TIP3P~\cite{jorgensen83} water model was used to solvate the system and Ions are described by the parameters derived by Aqvist~\cite{aqvist90}.
Simulation was performed for 200~ns, and the last 100~ns were used for the analysis. Simulation was carried out within the NPT ensemble using the GROMACS 5.0.4 package~\cite{abraham2015gromacs}. Timestep of 2~fs was used with the leapfrog integrator. The Nos\'{e}--Hoover thermostat~\cite{nose84,hoover85} was used with reference temperature of 303~K and a relaxation time constant of 0.5~ps; lipids and water plus ions were coupled separately to the heat bath. Pressure was kept constant at 1.013~bar using a semi--isotropic Parrinello--Rahman
barostat~\cite{parrinello81} with a time constant of 10.0~ps. Long-range electrostatic interactions were calculated using the PME method~\cite{darden93,essman95}. A real space cut-off of 1.0~nm was employed with grid spacing of 0.12~nm in the reciprocal space. Lennard-Jones potentials were cut off at 1.4~nm, with a dispersion correction applied to both energy and pressure. All covalent bonds in lipids were constrained using the LINCS algorithm~\cite{hess97}, whereas water molecules were constrained using SETTLE~\cite{miyamoto92}. Twin-range cutoffs, 1.0~nm and 1.6~nm, were used for the neighbor lists with the long-range neighbor list updated every 10 steps.

\todo{Other systems to be written by Piggot}
